S-Tipping vs B-Tipping

### 2018-03-30 paper/paper.Rmd
sketching outline and more boilerplate

  It consists of two paragraphs.

journal: Journal of Mathematical Biology
bibliography: mybibfile.bib
output: rticles::elsevier_article

@@

>>>>

layout:  3p # review = doublespace, 3p = singlespace, 5p = two-column
preamble: |
  \newcommand{\ud}{\mathrm{d}}
  \usepackage[nomarkers]{endfloat}
  \linenumbers
  \usepackage{setspace}
  \doublespacing
journal: Journal of Mathematical Biology
bibliography: refs.bib
csl: journal-of-mathematical-biology.csl
output: rticles::elsevier_article

@@

# Introduction

Critical transistions.

Two flavors: S tipping vs B tipping

Dimensionality.  Absense of an explicit model often makes it difficult to intuit if and how a complex ecosystem can be intepreted in terms of this simple one-dimensional bifurcation process.  Lack of clarity about what defines the "state" and what defines the "parameters" leads to confusion.  These issues are easily glossed over...

Focus on a prominent example from lake ecosystems.

# Model

@Carpenter2008

# Analysis

Dimensionality reduction

## Implications for Resilience and Early Warning

# Discussion

# Acknowledgements

CB acknowledges support in part from USDA National Institute of Food and Agriculture, Hatch project CA-B-INS-0162-H.

\newpage

# References
